---
title: "Introduction to PromiseLand's Currency Forecasts"
author: 
- Caleb Ong Jun Yi
date: "Last Updated: `r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
    number_sections: yes
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\LARGE\includegraphics[width=12cm]{Logo_O.png}\\[\bigskipamount]}
  - \posttitle{\end{center}}
  - \usepackage{graphicx}
  - \usepackage{lastpage}
  - \usepackage{wrapfig}
  - \usepackage{caption}
  - \usepackage{fancyhdr}
  - \input{insbox} 
  - \pagestyle{fancy}
  - \renewcommand{\headrulewidth}{0.4pt}
  - \renewcommand{\footrulewidth}{0.4pt}
  - \setlength{\headheight}{27pt}
  - \addtolength{\topmargin}{-10pt}
  - \fancyhead[L]{\includegraphics[width=1cm]{Logo(Grape)_Blue.png}}
  - \fancyhead[R]{\small \leftmark}
  - \fancyhead[C]{\small Page {\thepage} of \pageref{LastPage}}
  - \fancyfoot[C]{\tiny This document is prepared by PromiseLand Independent Pte Ltd. It does not reflect any views from any other agency, organization, employer or company. This document is for information only. It does not constitute an offer or solicitation to deal in units of any investments. It was prepared with no consideration for any specific financial situation, objective or need. No warranty is given and no liability is accepted for any loss arising directly or indirectly as a result of any action taken by a person acting on the information, opinion, forecast, or estimate contained herein. Past performance, prediction, projection or forecast of any economic trends or financial markets are not necessarily indicative of the future or likely performance of any investments. Please read the prospectus of the funds to understand the risks associated in investing in the fund, which may be obtained from PromiseLand Independent Pte. Ltd. or directly from the relevant entity. Potential investors may wish to seek advice from a financial adviser before making any investment decision. This advertisement has not been reviewed by the Monetary Authority of Singapore.}
mainfont: Times New Roman
fontsize: 11pt
---

\newpage

\setcounter{tocdepth}{2}
\tableofcontents

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center', fig.width = 10, fig.height = 6)
```

```{r, load plots, include=FALSE, message=FALSE}
load('stockClientPlot.RData')

library(magrittr)
library(ggplot2)
library(ggthemes)
```

\newpage
 
# Introduction

Currency forecasting is the process of predicting future trends and levels of currencies. Such forecasts can aid in setting short-term
active investment decisions. For instance, when investing in foreign markets, clients can decide if they would like to take on the currency exposures of such markets, or to hedge away the currency risk.


Our approach to currency forecasting is based on technical analysis and advanced statistical modelling. Currencies are subject to high levels of trading; market participants are likely to have already utilised external data to establish their positions. Accordingly, we believe that such information would already been factored into exchange rates. The nature of currency price data is such that they have a tendency to exhibit price patterns that are repeatable and recognisable. 

Clients can use the expected currency forecasts to aid in their short-term investment decision­ making process.

# Methodology


The latest, cutting-edge data analytics and forecasting tools are employed. Advanced time series modelling are employed in the currency forecasting models. Past and current values are analysed to identify any relationships that can explain future currency movements. Once the models are finalized, one step ahead, short term forecasts of one month are made. When new currency data is released, it is incorporated into the models. The models are then updated for the next round of forecasts.

\newpage

# Illustrative Example

The data of the USDJPY currency pair is used to illustrate some of the analyses that are conducted.

Extensive statistical modelling is conducted on past price data to identify factors that could contribute to future price levels and trends. For instance, we incorporate a considerable amount of lagged values to determine the effect of past values on future expected price levels. We also incorporate rolling averages of price levels and volatility into the analysis.

```{r, show frontplot, echo=FALSE, message=FALSE, warning=FALSE}
frontplot
```

\newpage

After extensive time series analysis are conducted on all currency pairs, the expected daily returns of all sectors at prior particular points in time are then predicted.

The predicted expected returns of all sectors are then compared to the actual returns to assess the effectiveness of the models. Models with the best ability to generalize predictions across all currency pairs are then selected.

```{r, show testplot, echo=FALSE, message=FALSE, warning=FALSE}
testplot
```




\newpage

Once the optimal models are selected, a one month ahead forecast is made.

```{r, futureplot, echo=FALSE, message=FALSE, warning=FALSE}
futureplot
```

Given that forecasts are made a month into the future, the models are updated for the next round of forecasts by incorporating the latest currency data on a monthly basis, or when requested.

\newpage

# Risks

The models incorporate only all available information up to the time the forecast is made, which include the latest currency data. The occurrence of unexpected market events in the periods since then can affect future currency rates. As with all financial models, they provide only a generalization of what an outcome is expected to be.

# Ending Notes

Clients are reminded to diligently monitor their holdings. Please contact your financial advisor for the latest currency forecasts, or if you have any questions. Alternatively, you may contact us at +65 6505 4100, or email us at <enquiries@promiseland.com.sg>.

